MCC Models

### 2019-03-20 papers/full_paper/models.Rmd
child noisy model predictions

@@

var allData = dataFromR.ex3data

@@

```{r predictions pragmatic model ex3 children}
child_ex3_pragm_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.predictions , sep='\n'),
  data =list(ex3data = ex3_model_data),
  data_var = "dataFromR"
)

# model predictions
child_ex3_pragm_model_predictions <- child_ex3_pragm_model %>%
  separate(`0`, into = c("age", "speaker", "alignment","correct"), sep="/")%>%
  mutate(value = `1`,
         model="pragmatic",
         age = as.numeric(age))%>%
  select(-`1`)
```

@@

```{r predictions prior only model ex3 children}
child_ex3_prior_only_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, child.ex3.prior.only.predictions , sep='\n'),
  data =list(ex3data = ex3_model_data),
  data_var = "dataFromR"
)

# model predictions
child_ex3_prior_only_model_predictions <- child_ex3_prior_only_model %>%
  separate(`0`, into = c("age", "speaker", "alignment","correct"), sep="/")%>%
  mutate(value = `1`,
         model="prior_only",
         age = as.numeric(age))%>%
  select(-`1`)

@@

```{r predictions flat prior model ex3 children}
child_ex3_flat_prior_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.predictions , sep='\n'),
  data =list(ex3data = ex3_model_data),
  data_var = "dataFromR")

# model predictions
child_ex3_flat_prior_model_predictions <- child_ex3_flat_prior_model %>%
  separate(`0`, into = c("age", "speaker", "alignment","correct"), sep="/")%>%
  mutate(value = `1`,
         model="flat_prior",
         age = as.numeric(age))%>%
  select(-`1`)

@@

```{r plot model predictions ex3 children}
child_model_predictions <- bind_rows(
  child_ex3_pragm_model_predictions,
  child_ex3_flat_prior_model_predictions,
  child_ex3_prior_only_model_predictions
  )

@@

ggplot(child_model_predictions)+
  #geom_jitter(data = plot_child_ex3_data, aes(x = age_num, y = mean), width = .025,height = .025, alpha = .2)+
  geom_line(aes(x = age, y = value, col = model), size = 1, alpha = 1, linetype = 1) + 
  geom_smooth(data = child_ex3_data, aes(x = age_num, y = correct_inf), col = "black", size = 0.6, method = "loess", span = 1,  se = T,  alpha = .5)+
  #geom_hline(yintercept = 0.5, lty=2)+
  labs(y="proportion more informative")+
  ylim(-0.05,1.05)+
  facet_grid(speaker~alignment)+
  theme_few()+
  scale_color_manual(name="Model",
                     breaks=c("pragmatic","flat_prior","prior_only"),
                     values= c("#859900","#6c71c4","#b58900"))+
  scale_fill_manual(name="Model",
                     breaks=c("pragmatic","flat_prior","prior_only"),
                     values= c("#859900","#6c71c4","#b58900"))

@@

child_cor_model <- child_model_predictions %>%
  mutate(age = ifelse(age<4,"3","4"))%>%
  group_by(model,speaker,alignment, age)%>%
  summarise(Model = mean(value))

child_cor_plot <- child_cor_model %>%
  ungroup()%>%
  mutate(Data = rep(child_cor_data$Data,3),
         Data_ci_lower = rep(child_cor_data$Data_ci_lower,3),
         Data_ci_upper  =rep( child_cor_data$Data_ci_upper,3))

>>>>

#### Parameter free

@@

var allData = dataFromR.allData

@@

```{r predictions pragmatic model ex3 children}
child_ex3_pragm_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.predictions , sep='\n'),
  data =list(allData = ex3_model_data),
  data_var = "dataFromR"
)

# model predictions
child_ex3_pragm_model_predictions <- child_ex3_pragm_model %>%
  separate(`0`, into = c("age", "speaker", "alignment","correct"), sep="/")%>%
  mutate(mean = `1`,
         ci_lower = mean,
         ci_upper = mean,
         model="pragmatic",
         age = as.numeric(age))%>%
  select(-`1`)
```

#### Noise parameter

```{r}
child.ex3.rsa.predictions.noise <-'

var allData = dataFromR.allData

  var noise = uniformDrift({a: 0, b: 1, width: 0.1})

    observe(noisyModelPredictions, row.correct_inf)

    return  [row.age_num + "/" + row.speaker + "/" + row.alignment, Math.exp(noisyModelPredictions.score(1))]

 return extend(_.fromPairs(output), {noise: noise})

```{r}
# child_ex3_pragm_model_noise<- webppl(
#   program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.predictions.noise , sep='\n'),
#   data =list(allData = ex3_model_data),
#   data_var = "dataFromR",
#   model_var = "model",
#   chains = 4,
#   cores = 4,
#   inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
# )%>%
#    saveRDS("../../stats/saves/child_ex3_pragm_model_noise.rds")

# model predictions
child_ex3_pragm_model_predictions_noise <- readRDS("../../stats/saves/child_ex3_pragm_model_noise.rds") %>%
  filter(!(Parameter %in% c("noise"))) %>%
  separate(Parameter, into = c("age", "speaker", "alignment"), sep="/")%>%
  mutate(model = "pragmatic_noise")%>%
  group_by(model, age,alignment,speaker) %>%
  summarise(mean = estimate_mode(value), 
            ci_lower = hdi_lower(value), 
            ci_upper =hdi_upper(value))%>%
  ungroup()%>%
  mutate(age = as.numeric(age))

## noise parameter
child_ex3_pragm_model_noise_param <- readRDS("../../stats/saves/child_ex3_pragm_model_noise.rds") %>%
  filter(Parameter %in% c("noise"))  %>%
  summarise(mean = estimate_mode(value), 
            ci_lower = hdi_lower(value),
            ci_upper = hdi_upper(value))

@@

```{r predictions prior only model ex3 children}
child_ex3_prior_only_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, child.ex3.prior.only.predictions , sep='\n'),
  data =list(allData = ex3_model_data),
  data_var = "dataFromR"
)

# model predictions
child_ex3_prior_only_model_predictions <- child_ex3_prior_only_model %>%
  separate(`0`, into = c("age", "speaker", "alignment","correct"), sep="/")%>%
  mutate(mean = `1`,
         model="prior_only",
         age = as.numeric(age))%>%
  select(-`1`)

@@

```{r predictions flat prior model ex3 children}
child_ex3_flat_prior_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.predictions , sep='\n'),
  data =list(allData = ex3_model_data),
  data_var = "dataFromR")

# model predictions
child_ex3_flat_prior_model_predictions <- child_ex3_flat_prior_model %>%
  separate(`0`, into = c("age", "speaker", "alignment","correct"), sep="/")%>%
  mutate(mean = `1`,
         model="flat_prior",
         age = as.numeric(age))%>%
  select(-`1`)

@@

```{r plot model predictions ex3 children}
child_model_predictions <- bind_rows(
  child_ex3_pragm_model_predictions_noise,
  child_ex3_pragm_model_predictions,
  child_ex3_flat_prior_model_predictions,
  child_ex3_prior_only_model_predictions
  )

@@

ggplot(child_model_predictions)+
  #geom_jitter(data = plot_child_ex3_data, aes(x = age_num, y = mean), width = .025,height = .025, alpha = .2)+
  geom_ribbon(aes(x = age, ymin = ci_lower, ymax = ci_upper, fill = model), alpha = .4) +
  geom_line(aes(x = age, y = mean, col = model), size = 1, alpha = 1, linetype = 1) + 
  geom_smooth(data = child_ex3_data, aes(x = age_num, y = correct_inf), col = "black", size = 0.6, method = "loess", span = 1,  se = T,  alpha = .5)+
  #geom_hline(yintercept = 0.5, lty=2)+
  labs(y="proportion more informative")+
  ylim(-0.05,1.05)+
  facet_grid(speaker~alignment)+
  theme_few()+
  scale_color_manual(name="Model",
                     breaks=c("pragmatic","pragmatic_noise","flat_prior","prior_only"),
                     values= c("#859900","#00afaf","#6c71c4","#b58900"))+
  scale_fill_manual(name="Model",
                     breaks=c("pragmatic","pragmatic_noise","flat_prior","prior_only"),
                     values= c("#859900","#00afaf","#6c71c4","#b58900"))

@@

child_cor_model <- child_model_predictions %>%
  mutate(age = ifelse(age<4,"3","4"))%>%
  group_by(model,speaker,alignment, age)%>%
  summarise(Model = mean(mean))

child_cor_plot <- child_cor_model %>%
  ungroup()%>%
  mutate(Data = rep(child_cor_data$Data,4),
         Data_ci_lower = rep(child_cor_data$Data_ci_lower,4),
         Data_ci_upper  =rep( child_cor_data$Data_ci_upper,4))
